### 2019-04-04 papers/journal/encoding.tex
added clarification for the 3 problems and 4 envodings

%\externaldocument{sat-table}
%\externaldocument{smt-table}
%\externaldocument{qbf-table}
\noindent In the previous section, we have discussed four problems.
%
In this section we will present encodings fof the
$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
%
We will start with the $\fsmt$ search encoding and later present the
contrast with the $\fbmc$ encoding.

>>>>

%\externaldocument{sat-table}
%\externaldocument{smt-table}
%\externaldocument{qbf-table}
\noindent In the previous section, we have discussed four problems, $\fbmc$ search, $\fsmt$ search, $\fqbf$ search and synthesis problem.
%
In this section we will present encodings for each of them.
%
Although the underlying technique for $\fbmc$ and $\fsmt$ search varies, the encoding is very similar. 
%
So, instead of presenting both 
%$\fsmt$ search, $\fbmc$ search, $\fqbf$ search and synthesis problems.
%
we will start with the complete $\fsmt$ search encoding and present only the relevant part of the the $\fbmc$ encoding to show a contrast.
%contrast with the $\fbmc$ encoding.
